---
title: "TATA _ opensource data analysis" 
author: "KRM" 
date: "`r Sys.Date()`" 
output: word_document
---

EXPLAROTARY ANALYSIS (EDA)

# Load packages

# Load the data

```{r}
library("tidyverse")
library("readxl")
library("dplyr")

```

```{r}
retail_data<-read_excel("H:/R programming/TATA/Online Retail.xlsx")
retail_data
```

# Number of rows of the data

```{r}
nrow(retail_data)
```

# Number of Variables or columns of the data

```{r}
ncol(retail_data)
```

# Variables or column names of the data

```{r}
colnames(retail_data)
```

# Variables or column names of the data

```{r}
head(retail_data)
```

# View the sample data

```{r}

View(retail_data)

```

# Structure of the data

```{r}
str(retail_data)

```

# summary of the data statistics

```{r}

summary(retail_data)

```

```{r}
variable.names(retail_data)
```

find UNIQE value of Variable country

```{r}
unique(retail_data$Country)
```

```{r}

# number of rows annd columns/ variables of the data 
dim(retail_data)

```

```{r}

       max(retail_data$InvoiceDate)
      max(retail_data$Country)


```

```{r}

summary(retail_data)

```

**Data cleaning - creating subset, revmoving quantity zero and unit price less than 1**

```{r}
df <- filter(retail_data, Quantity>=0 & UnitPrice >=1)
df
```

**Adding Revenue column to data by mutate function, calculation done.**

```{r}
revenue_data<-mutate(df,revenue = (df$Quantity * df$Quantity))
revenue_data




```


TQ **1. 1 Which region generates the highest revenue and which region generates the lowest ?**

```{r}
country_profit<- max(revenue_data$Country)
country_profit
max(revenue_data$revenue)

min(revenue_data$revenue)
min(revenue_data$Country)


```

**TQ \*\*1. 2 Did customers based have significant impact on revenue ?**

```{r}
aggregate(revenue~Country+,revenue_data,sum)
```

```{r}
aggregate(revenue~Country+CustomerID,revenue_data,sum)

```
